A convenient, flexible and intuitive analytic expression for the metallicity-dependent cosmic star formation rate

### 2022-06-09 src/tex/ms.tex
[showyourwork] overleaf sync

We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.   
To this end we use the publicly available rapid binary population synthesis simulations as presented in \cite{vanson+2022}. These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}. \COMPAS is based on algorithms  model the evolution of massive stars in binary systems following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems.

>>>>

We will now demonstrate the flexibility of our analytical model by systematically varying each of the parameters in our fiducial \SFRDzZ model, and investigate their effect on the local mass distribution of BBH mergers originating from isolated binaries.   
To this end we use the publicly available rapid binary population synthesis simulations as presented in \cite{vanson+2022}. These simulations were run using version v02.19.04 of the open source \COMPAS suite \citep{COMPAS_method} \footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}. \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002}, based on detailed evolutionary models by \citet{Pols+1998}.
We use the framework described in \cite{vanson+2022} to compute local merger rates of BBH systems.
